Associations between chlorophyll \emph{a} and various microcystin-LR health advisory Concentrations

### 2016-05-31 manuscript/f1000_submission/manuscript.Rmd
update

knit_hooks$set(tab.cap = function(before, options, envir) {
                  if(!before) { 
                    paste('\n\n:', options$tab.cap, sep='') 
                  }
                })
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == FALSE) {
    x
  } else
    default_output_hook(x,options)
})
```

@@

total_accuracy<-NULL
total_accuracy$epa_child<-round((child_conmat[1,1]+child_conmat[2,2])/
  sum(child_conmat),2)
total_accuracy$who_drink<-round((who_drink_conmat[1,1]+who_drink_conmat[2,2])/
  sum(who_drink_conmat),2)
total_accuracy$epa_adult<-round((adult_conmat[1,1]+adult_conmat[2,2])/
  sum(adult_conmat),2)
total_accuracy$who_rec<-round((who_rec_conmat[1,1]+who_rec_conmat[2,2])/
  sum(who_rec_conmat),2)

fn_percent<-NULL
fn_percent$epa_child<-round((child_conmat[1,2])/
  sum(child_conmat),2)
fn_percent$who_drink<-round((who_drink_conmat[1,2])/
  sum(who_drink_conmat),2)
fn_percent$epa_adult<-round((adult_conmat[1,2])/
  sum(adult_conmat),2)
fn_percent$who_rec<-round((who_rec_conmat[1,2])/
  sum(who_rec_conmat),2)

@@

In the 2007 NLA, microcystin-LR concentrations ranged from `r min(nla_dat$MCYST_TL_UGL,na.rm=T)` to `r max(nla_dat$MCYST_TL_UGL, na.rm=T)` $\mu$g/L.  Microcystin-LR concentrations of 0.05 $\mu$g/L represent the detection limits.  Any value greater than that indicates the presence of microcystin-LR.  Of those lakes with microcystin, the median concentration was `r round(median(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>0.05],na.rm=T), 2)`$\mu$g/L and the mean was `r round(mean(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>0.05],na.rm=T), 2)`$\mu$g/L.  Of all lakes sampled, `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=0.3])/length(nla_dat$MCYST_TL_UGL)),1)`% of lakes exceeded the USEPA Child level, `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=1.6])/length(nla_dat$MCYST_TL_UGL)),1)`% of lakes exceeded the USEPA Adult level, `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=1])/length(nla_dat$MCYST_TL_UGL)),1)`% of lakes exceeded the WHO Drinking level, and `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=2])/length(nla_dat$MCYST_TL_UGL)),1)`% of lakes exceeded the WHO Recreational level. For chlorophyll *a*, the range was `r min(nla_dat$CHLA,na.rm=T)` to `r max(nla_dat$CHLA, na.rm=T)` $\mu$g/L.  All lakes had reported chlorophyll *a* concentrations that exceeded detection limits.  The median concentration was `r median(nla_dat$CHLA,na.rm=T)` $\mu$g/L and the mean was `r round(mean(nla_dat$CHLA,na.rm=T),2)` $\mu$g/L.  The associations between chlorophyll *a* and the upper confidence interval across a range of conditional probability values are shown in Table \ref{tab:mc_chla_table}.  Specific chlorophyll *a* concentrations that are associated with greater than even odds of exceeding the advisory levels were `r mc_chla[1]`, `r mc_chla[2]`, `r mc_chla[3]`, and `r mc_chla[4]`$\mu$g/L for 0.3, 1.0, 1.6, and 2.0 $\mu$g/L advisory levels, respectively (Table \ref{tab:mc_chla_table} & Figure \ref{fig:multi_cp_plot}).

>>>>

knit_hooks$set(tab.cap = function(before, options, envir) {
                  if(!before) { 
                    paste('\n\n:', options$tab.cap, sep='') 
                  }
                })
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == FALSE) {
    x
  } else
    default_output_hook(x,options)
})

set.seed(2042016)
```

@@

total_accuracy<-NULL
total_accuracy$epa_child<-round((child_conmat[1,1]+child_conmat[2,2])/
  sum(child_conmat[1:2,1:2]),2)
total_accuracy$who_drink<-round((who_drink_conmat[1,1]+who_drink_conmat[2,2])/
  sum(who_drink_conmat[1:2,1:2]),2)
total_accuracy$epa_adult<-round((adult_conmat[1,1]+adult_conmat[2,2])/
  sum(adult_conmat[1:2,1:2]),2)
total_accuracy$who_rec<-round((who_rec_conmat[1,1]+who_rec_conmat[2,2])/
  sum(who_rec_conmat[1:2,1:2]),2)

fn_percent<-NULL
fn_percent$epa_child<-round((child_conmat[1,2])/
  sum(child_conmat[1:2,1:2]),2)
fn_percent$who_drink<-round((who_drink_conmat[1,2])/
  sum(who_drink_conmat[1:2,1:2]),2)
fn_percent$epa_adult<-round((adult_conmat[1,2])/
  sum(adult_conmat[1:2,1:2]),2)
fn_percent$who_rec<-round((who_rec_conmat[1,2])/
  sum(who_rec_conmat[1:2,1:2]),2)

@@

In the 2007 NLA, microcystin-LR concentrations ranged from `r min(nla_dat$MCYST_TL_UGL,na.rm=T)` to `r max(nla_dat$MCYST_TL_UGL, na.rm=T)` $\mu$g/L.  Microcystin-LR concentrations of 0.05 $\mu$g/L represent the detection limits.  Any value greater than that indicates the presence of microcystin-LR.  Of those lakes with microcystin, the median concentration was `r round(median(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>0.05],na.rm=T), 2)`$\mu$g/L and the mean was `r round(mean(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>0.05],na.rm=T), 2)`$\mu$g/L.  Of all lakes sampled, `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=0.3])/length(nla_dat$MCYST_TL_UGL)),1)`% of lakes exceeded the USEPA Child level, `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=1.6])/length(nla_dat$MCYST_TL_UGL)),1)`% of lakes exceeded the USEPA Adult level, `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=1])/length(nla_dat$MCYST_TL_UGL)),1)`% of lakes exceeded the WHO Drinking level, and `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=2])/length(nla_dat$MCYST_TL_UGL)),1)`% of lakes exceeded the WHO Recreational level. For chlorophyll *a*, the range was `r min(nla_dat$CHLA,na.rm=T)` to `r max(nla_dat$CHLA, na.rm=T)` $\mu$g/L.  All lakes had reported chlorophyll *a* concentrations that exceeded detection limits.  The median concentration was `r median(nla_dat$CHLA,na.rm=T)` $\mu$g/L and the mean was `r round(mean(nla_dat$CHLA,na.rm=T),2)` $\mu$g/L.  The associations between chlorophyll *a* and the upper confidence interval across a range of conditional probability values are shown in Table \ref{tab:mc_chla_table}.  Specific chlorophyll *a* concentrations that are associated with greater than even odds of exceeding the advisory levels were `r mc_chla[5,1]`, `r mc_chla[5,2]`, `r mc_chla[5,3]`, and `r mc_chla[5,4]`$\mu$g/L for 0.3, 1.0, 1.6, and 2.0 $\mu$g/L advisory levels, respectively (Table \ref{tab:mc_chla_table} & Figure \ref{fig:multi_cp_plot}).

### 2016-05-31 manuscript/f1000_submission/manuscript.tex
update

In the 2007 NLA, microcystin-LR concentrations ranged from 0.05 to 225
\(\mu\)g/L. Microcystin-LR concentrations of 0.05 \(\mu\)g/L represent
the detection limits. Any value greater than that indicates the presence
of microcystin-LR. Of those lakes with microcystin, the median
concentration was 0.51\(\mu\)g/L and the mean was 3.17\(\mu\)g/L. Of all
lakes sampled, 21\% of lakes exceeded the USEPA Child level, 8.8\% of
lakes exceeded the USEPA Adult level, 11.7\% of lakes exceeded the WHO
Drinking level, and 7.3\% of lakes exceeded the WHO Recreational level.
For chlorophyll \emph{a}, the range was 0.07 to 936 \(\mu\)g/L. All
lakes had reported chlorophyll \emph{a} concentrations that exceeded
detection limits. The median concentration was 7.79 \(\mu\)g/L and the
mean was 29.63 \(\mu\)g/L. The associations between chlorophyll \emph{a}
and the upper confidence interval across a range of conditional
probability values are shown in Table \ref{tab:mc_chla_table}. Specific
chlorophyll \emph{a} concentrations that are associated with greater
than even odds of exceeding the advisory levels were 0.07, 0.07, 2.98,
and 10.67\(\mu\)g/L for 0.3, 1.0, 1.6, and 2.0 \(\mu\)g/L advisory
levels, respectively (Table \ref{tab:mc_chla_table} \& Figure
\ref{fig:multi_cp_plot}).

@@

The chlorophyll \emph{a} cutoffs may be used to predict whether or not a
lake exceeds the microcystin-LR health advisories. Doing so allows us to
compare the accuracy of the prediction as well as evaluate false
negatives. Total accuracy of the four cutoffs predicting microcystin-LR
exceedances were 19\% for the USEPA children's advisory, 21\% for the
WHO drinking water advisory, 22\% for the USEPA adult advisory, and 23\%
for the WHO regreational advisory (Tables \ref{tab:child_conmat_table},
\ref{tab:who_drink_conmat_table}, \ref{tab:adult_conmat_table}, \&
\ref{tab:who_rec_conmat_table}). However, total accuracy is only one
part of the prediction performace with which we are concerned.

When using the chlorophyll \emph{a} cutoffs as an indicator of
microcystin-LR exceedances, the error that should be avoided is
predicting that no exceedance has occurred when in fact it has. In other
words, we would like to avoid Type II errors and minimize the proportion
of false negatives. For the four chlorophyll \emph{a} cut-offs we had a
proportion of false negatives of 2\%, 2\%, 1\%, and 1\% for the USEPA
children's, the WHO drinking water, the USEPA adult, and the WHO
recreational advisories, respectively. In each case we missed less than
10\% of the lakes that in fact exceeded the microcystin-LR advisory.
While this method performs well with regard to the false negative
percentage, it is possible that is a relic of the NLA dataset and
testing with additional data would allow us to confirm this result.

@@

This is the case as the probability of exceeding each of the four tested
health advisory levels increases as a function of chlorophyll \emph{a}
concentration (Figure \ref{fig:multi_cp_plot}). We used this association
to identify chlorophyll \emph{a} concentrations that are associated with
a range of probabilities of exceeding a given health advisory level
(Table \ref{tab:mc_chla_table}). For the purposes of this discussion we
focus on a conditional probability of 50\% or greater (i.e., greater
than even odds to exceed a health advisory level). The 50\% conditional
probability chlorophyll \emph{a} thresholds represents 27.9\%, 11.3\%,
9\%, and 6.9\% of sample lakes for the USEPA Child, the WHO Drinking,
the USEPA Adult, and the WHO recreational levels, respecitvely.

@@

\begin{table}[ht]
\caption{Chlorophyll \textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration.} 
\label{tab:mc_chla_table}
\begin{tabular}{rrrrr}
  \hline
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO Recreational \\ 
  \hline
0.10 & 0.07 & 0.07 & 0.07 & 1.22 \\ 
  0.20 & 0.07 & 4.43 & 11.80 & 20.00 \\ 
  0.30 & 2.98 & 20.43 & 31.40 & 53.64 \\ 
  0.40 & 10.67 & 42.24 & 66.96 & 82.22 \\ 
  0.50 & 23.36 & 66.96 & 83.52 & 105.84 \\ 
  0.60 & 38.30 & 103.20 & 133.20 & 155.52 \\ 
  0.70 & 65.60 & 166.63 & 871.20 & 216.00 \\ 
  0.80 & 117.50 & 338.40 & 871.20 & 871.20 \\ 
  0.90 & 167.04 & 516.00 & 871.20 & 871.20 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory.} 
\label{tab:who_drink_conmat_table}
\begin{tabular}{rrrr}
  \hline
 & Not Exceed & Exceed & Row Totals \\ 
  \hline
Not Exceed & 839 &  77 & 916 \\ 
  Exceed &  68 &  44 & 112 \\ 
  Column Totals & 907 & 121 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory.} 
\label{tab:who_rec_conmat_table}
\begin{tabular}{rrrr}
  \hline
 & Not Exceed & Exceed & Row Totals \\ 
  \hline
Not Exceed & 910 &  52 & 962 \\ 
  Exceed &  43 &  23 &  66 \\ 
  Column Totals & 953 &  75 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

In the 2007 NLA, microcystin-LR concentrations ranged from 0.05 to 225
\(\mu\)g/L. Microcystin-LR concentrations of 0.05 \(\mu\)g/L represent
the detection limits. Any value greater than that indicates the presence
of microcystin-LR. Of those lakes with microcystin, the median
concentration was 0.51\(\mu\)g/L and the mean was 3.17\(\mu\)g/L. Of all
lakes sampled, 21\% of lakes exceeded the USEPA Child level, 8.8\% of
lakes exceeded the USEPA Adult level, 11.7\% of lakes exceeded the WHO
Drinking level, and 7.3\% of lakes exceeded the WHO Recreational level.
For chlorophyll \emph{a}, the range was 0.07 to 936 \(\mu\)g/L. All
lakes had reported chlorophyll \emph{a} concentrations that exceeded
detection limits. The median concentration was 7.79 \(\mu\)g/L and the
mean was 29.63 \(\mu\)g/L. The associations between chlorophyll \emph{a}
and the upper confidence interval across a range of conditional
probability values are shown in Table \ref{tab:mc_chla_table}. Specific
chlorophyll \emph{a} concentrations that are associated with greater
than even odds of exceeding the advisory levels were 23.36, 62.64,
83.52, and 103.9\(\mu\)g/L for 0.3, 1.0, 1.6, and 2.0 \(\mu\)g/L
advisory levels, respectively (Table \ref{tab:mc_chla_table} \& Figure
\ref{fig:multi_cp_plot}).

@@

The chlorophyll \emph{a} cutoffs may be used to predict whether or not a
lake exceeds the microcystin-LR health advisories. Doing so allows us to
compare the accuracy of the prediction as well as evaluate false
negatives. Total accuracy of the four cutoffs predicting microcystin-LR
exceedances were 75\% for the USEPA children's advisory, 86\% for the
WHO drinking water advisory, 89\% for the USEPA adult advisory, and 91\%
for the WHO regreational advisory (Tables \ref{tab:child_conmat_table},
\ref{tab:who_drink_conmat_table}, \ref{tab:adult_conmat_table}, \&
\ref{tab:who_rec_conmat_table}). However, total accuracy is only one
part of the prediction performace with which we are concerned.

When using the chlorophyll \emph{a} cutoffs as an indicator of
microcystin-LR exceedances, the error that should be avoided is
predicting that no exceedance has occurred when in fact it has. In other
words, we would like to avoid Type II errors and minimize the proportion
of false negatives. For the four chlorophyll \emph{a} cut-offs we had a
proportion of false negatives of 9\%, 7\%, 6\%, and 5\% for the USEPA
children's, the WHO drinking water, the USEPA adult, and the WHO
recreational advisories, respectively. In each case we missed less than
10\% of the lakes that in fact exceeded the microcystin-LR advisory.
While this method performs well with regard to the false negative
percentage, it is possible that is a relic of the NLA dataset and
testing with additional data would allow us to confirm this result.

@@

This is the case as the probability of exceeding each of the four tested
health advisory levels increases as a function of chlorophyll \emph{a}
concentration (Figure \ref{fig:multi_cp_plot}). We used this association
to identify chlorophyll \emph{a} concentrations that are associated with
a range of probabilities of exceeding a given health advisory level
(Table \ref{tab:mc_chla_table}). For the purposes of this discussion we
focus on a conditional probability of 50\% or greater (i.e., greater
than even odds to exceed a health advisory level). The 50\% conditional
probability chlorophyll \emph{a} thresholds represents 27.9\%, 12.1\%,
9\%, and 7.3\% of sample lakes for the USEPA Child, the WHO Drinking,
the USEPA Adult, and the WHO recreational levels, respecitvely.

@@

\begin{table}[ht]
\caption{Chlorophyll \textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration.} 
\label{tab:mc_chla_table}
\begin{tabular}{rrrrr}
  \hline
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO Recreational \\ 
  \hline
0.10 & 0.07 & 0.07 & 0.07 & 1.65 \\ 
  0.20 & 0.07 & 4.30 & 9.52 & 20.52 \\ 
  0.30 & 2.91 & 18.72 & 25.76 & 53.64 \\ 
  0.40 & 10.88 & 38.02 & 65.60 & 82.22 \\ 
  0.50 & 23.36 & 62.64 & 83.52 & 103.90 \\ 
  0.60 & 39.80 & 94.93 & 114.62 & 155.52 \\ 
  0.70 & 65.60 & 125.40 & 273.60 & 871.20 \\ 
  0.80 & 125.28 & 314.61 & 871.20 & 871.20 \\ 
  0.90 & 197.00 & 516.00 & 871.20 & 871.20 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory.} 
\label{tab:who_drink_conmat_table}
\begin{tabular}{rrrr}
  \hline
 & Not Exceed & Exceed & Row Totals \\ 
  \hline
Not Exceed & 833 &  75 & 908 \\ 
  Exceed &  74 &  46 & 120 \\ 
  Column Totals & 907 & 121 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory.} 
\label{tab:who_rec_conmat_table}
\begin{tabular}{rrrr}
  \hline
 & Not Exceed & Exceed & Row Totals \\ 
  \hline
Not Exceed & 908 &  50 & 958 \\ 
  Exceed &  45 &  25 &  70 \\ 
  Column Totals & 953 &  75 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

### 2016-05-31 manuscript/manuscript.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% For more detailed article preparation guidelines, please see:
% http://f1000research.com/author-guidelines

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\bibliography{components/manuscript}

\begin{document}

%Still need to figure out how to get corresponding author on here.
\title{\textit{F1000Research} Associations between chlorophyll \emph{a} and various microcystin-LR
health advisory Concentrations}
\author[1]{Jeffrey W. Hollister}
\author[1]{Betty J. Kreakie}
\affil[1]{}

\maketitle
\thispagestyle{fancy}

\begin{abstract}

\end{abstract}

\clearpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Original default rstudio/pandoc latex file
%% upated by @jhollist 09/15/2014
%% inspired by @cboetting https://github.com/cboettig/template and
%% @rmflight blog posts:
%% http://rmflight.github.io/posts/2014/07/analyses_as_packages.html 
%% http://rmflight.github.io/posts/2014/07/vignetteAnalysis.html).  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
% Redefine \includegraphics so that, unless explicit options are
% given, the image width will not exceed the width of the page.
% Images get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother
\let\Oldincludegraphics\includegraphics
{%
 \catcode`\@=11\relax%
 \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
}%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Associations between chlorophyll a and various microcystin-LR health advisory Concentrations},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Changes borrowed from @cboettig, added by @jhollist 
% A modified page layout 
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
\usepackage{lineno} % add 
  \linenumbers % turns line numbering on 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Packages and layout changes by @jhollist 09/15/2014
\usepackage{ragged2e}
\usepackage[font=normalsize]{caption}
  \usepackage[doublespacing]{setspace}
\usepackage{parskip}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\today}
\lfoot{\thepage}
%%Changed default abstract width and added lines
\renewenvironment{abstract}{
  \hfill\begin{minipage}{1\textwidth}
  \rule{\textwidth}{1pt}\vspace{5pt}
  \normalsize
  \begin{justify}
  \bfseries\abstractname\vspace{5pt}
  \end{justify}}
  {\par\noindent\rule{\textwidth}{1pt}\end{minipage}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Associations between chlorophyll \emph{a} and various microcystin-LR
health advisory Concentrations}
\author{
Jeffrey W. Hollister
Betty J. Kreakie
}
\date{}

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Associations between chlorophyll \emph{a} and various microcystin-LR
health advisory Concentrations
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jeffrey W. Hollister \textsuperscript{*} \textsuperscript{1} 
Betty J. Kreakie \textsuperscript{1} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:hollister.jeff@epa.gov}{\nolinkurl{hollister.jeff@epa.gov}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

\end{singlespace}
